Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-27 sections/eval.tex
Update on Overleaf.

As depicted in Figure \ref{fig:spgemm_small}, Finch achieves comparable performance with TACO for inner-product. For large sparse matrices, as shown in Figure \ref{fig:spgemm_large}, Finch outperforms TACO with an average speedup of 1.05. It's worth mentioning that TACO's Gustavson's algorithm is hard-wired.

>>>>

As depicted in Figure \ref{fig:spgemm_small}, Finch achieves comparable performance with TACO for inner-product. For large sparse matrices, as shown in Figure \ref{fig:spgemm_large}, Finch outperforms TACO with an average speedup of 1.05. It's worth mentioning that TACO's Gustavson's algorithm is hard-wired whereas Finch's data structure-driving programming enables to systematically generate SpGEMM using explicit temporary, bytemap format, and matrix transposition.
